Evolved disk population of young brown dwarfs in \emph{Ophiuchus}\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}

### 2015-04-14 chIMACS/ms.tex
it compiles, but only with the tables in chapter 7 commented out
wow, I got everything to work!
add short figure captions to all figures.  formats better in the TOC

@@

\begin{figure}[ht!]
\caption{ Map of the region targeted by our survey.  The background grayscale image is the 2MASS NICER extinction map \citep{2008A&A...489..143L} from the COMPLETE project \citep{2006AJ....131.2921R}.  The solid line boundaries outline our regions of custom photometry with the following color scheme: \emph{blue solid lines} for the ISPI $JH$ catalog, \emph{green} for ISPI $K-$band, \emph{red} for \emph{c2deep}, \emph{magenta} for $I-$band, and \emph{yellow} for the custom $W-$band.  The large \emph{blue dashed} box defines our 2MASS $JH$ catalog.  The markers concentrated toward the right side of the image are from from previous surveys of \emph{Upper Scorpius}, with \emph{yellow squares:} \cite{2006AJ....131.3016S}.  \emph{Ophiuchus} members are concentrated around the high extinction core to the left of the image.  All known brown dwarfs detected by \emph{Herschel} are shown as \emph{green upward pointing triangles}, while brown dwarfs not detected by \emph{Herschel} are \emph{red downward pointing triangles}, \cite{2013A&A...559A.126A}. \emph{Cyan} circles are from \citet{2010ApJ...720.1374H}, and blue diamonds are from \citet{allers06}.\label{fig_star_chart}}
\centering
\includegraphics[scale=0.5]{chIMACS/figures/Ophiuchus_map}
\end{figure}

@@

\subsubsection{New: W filter}
Allers et al. (in prep) designed and implemented a custom filter centered at 1.4 $\mu$m, intermediate between the $J-$ and $H-$ atmospheric windows.  This filter is about 0.2 $\mu$m wide, cutting on near the long end of $J$ and cutting off near the short end of $H$.  This photometric band was designed to distinguish between the photospheric emission of late M and L spectral types and that of reddened FGK and early M spectral types.  Cool stars and brown dwarfs with late M spectral types demonstrate intrinsic water absorption in their photospheres.  There is a strong water absorption band centered around 1.4 $\mu$m.  The filter can also distinguish high$-z$ galaxies, which will not demonstrate intrinsic photospheric water absorption as brown dwarfs do.  The broad-band IJHK colors for FGK and early M sources are indistinguishable, while the $W-$filter band photometry shows a deficit in M-type spectra (Allers et al. \emph{in prep}).

@@

\input{chIMACS/tables/tbl_photomCatalog}

@@

\begin{figure}[ht!]
  \caption{Color-color cuts in $I-J$ vs $J-H$. The horizontal dashed line shows $I-J=2.85$.  The tilted dotted line demonstrates the selection for intrinsic blue $J-H$ colors ($<0.84156$), allowing for reddening.  The grayscale Hess diagram in the background shows the density of points in each color bin, constructed from 34469 sources with $I-$band detections.  The points in the upper left quadrant of the diagram meet the color cuts 2 and 3 from the list in Section \ref{sec_NIR_selection}.  The magenta circles are sources from \citet{allers06} that have spectral types between M6 and L2 \citep{2011ASPC..448..633G}.\label{fig_NIR_selection_JH}}
\centering
\includegraphics[scale=0.6]{chIMACS/figures/NIR_selection_allers_M6_L2}
\end{figure}

@@

\begin{figure}[ht!]
  \caption{Color-color cuts in $I-J$ vs $J-K$. The horizontal dashed line shows $I-J=2.85$.  The tilted dotted line demonstrates the selection for intrinsic blue $J-K$ colors ($<1.37662$), allowing for reddening.  The grayscale Hess diagram in the background shows the density of points in each color bin, constructed from 19733 sources with both $I-$ and $K-$band detections.  The points in the upper left quadrant of the diagram meet the color cuts 2 and 4 from the list in Section \ref{sec_NIR_selection}.  The square boxes plotted are sources from \citet{allers06} which have spectral types between M6 and L2 \citep{2011ASPC..448..633G}.\label{fig_NIR_selection_JK}}
\centering
\includegraphics[scale=0.6]{chIMACS/figures/NIR_selection_JK_allers_M6_L2}
\end{figure}

@@

\begin{figure}[ht!]
  \caption{$H-$band Magnitude cut.  The horizontal dashed line shows $H=13.99$.  The grayscale Hess diagram in the background shows the density of points in each color-magnitude bin, constructed from the entire 54373 point ISPI deep $JH$ source catalog.  The circles are sources from \citet{allers06} towards \emph{Ophiuchus}.  The two \citet{allers06} sources with $H>13.99$ have M8 spectral types, while the others are M6 or earlier \citep{2011ASPC..448..633G}. \label{fig_NIR_selection_H}}
\centering
\includegraphics[scale=0.6]{chIMACS/figures/NIR_selection_H_allers_oph}
\end{figure}

@@

\begin{figure}[ht!]
  \caption{$[3.6]-[5.8]$ vs $[3.6]-[8.0]$ color plot, demonstrating the mid-IR excess selection criterion.  The grayscale Hess diagram shows the density of 14095 sources in our sample possessing a 2 $\sigma$ detection in $[3.6]$ and a 2$\sigma$ detection in at least one of $[5.8]$, $[8.0]$, or $[24]$.  The horizontal dashed line is $[3.6]-[8.0]=0.21$, the vertical line is $[3.6]-[8.0]=0.08$ \citep{2006ApJ...651..502P}.  Sources meeting the criteria described in Section \ref{sec_midIR_selection} are primarily in the upper right quadrant.  Some sources with 3$\sigma$ $[24]$ detections are in the other quadrants.  The large colored circles are all sources from \citet{allers06}. \label{fig_midIR_selection}}
\centering
\includegraphics[scale=0.6]{chIMACS/figures/disk_selection_allers}
\end{figure}

@@

\begin{figure}[ht!]
	\caption{Histogram of the $Q$ value derived from $W-$band photometry.  The vertical dashed lines represent the boundaries of the selection method.  The dark colored region region interior to the boundaries indicates the 4\% of sources that were both detected in $W-$band and met the selection criteria.  The measured $Q-$values had to be at least 2$\;\sigma$ within the boundaries on either side, excluding some low-signal to noise ratio sources with nominal values between the boundaries and causing the blue shaded histogram to be below the light shaded parent population histogram.  \label{fig_Q_value_histogram}}
\centering
\includegraphics[scale=0.6]{chIMACS/figures/W_phot_sel_mgs}
\end{figure}

@@

\begin{figure}[ht!]
  \caption{$H-[3.6]$ and $K-[3.6]$ color cuts that comprise the ``mid-IR photosphere'' criterion.  \emph{Left panel-} The gray histrograms show the distribution of the 42268 sources in the catalog with a $[3.6]$ measurement, while the colored histogram shows the distribution of sources with $H-[3.6]$ \emph{consistent with} 0.8 (dashed vertical line) or greater.  The right panel shows an additional and more restrictive color cut applied only to the 18420 sources detected in both $K-$ band and $[3.6]$: these sources had to have $K-[3.6]$ exceed 0.49 (vertical dashed line) by 1 $\sigma$.  The final ``mid-IR photosphere criterion'' is the union of the color cuts in the left and right panels if $K-$band exists, otherwise it is just the sources satisfying the left panel.  \label{fig_midIR_phot_sel}}
\centering
\includegraphics[scale=0.6]{chIMACS/figures/midIR_phot_sel}
\end{figure}

@@

\input{chIMACS/tables/tbl_IMACSslitMasks.tex}

@@

\begin{figure}[ht!]
\caption{ Direct comparison spectra of the M7.25 young brown dwarf OPH1622-2405a, observed with IMACS from this work (solid blue line), and provided by K. Luhman (dotted black line, \citet{2007ApJ...659.1629L}).  The regions of telluric atmospheric absorption are indicated with light gray vertical bands.  \label{fig_oph1622_compare}}
\centering
\includegraphics[scale=0.9]{chIMACS/figures/oph1622-2405a_compare}
\end{figure}

@@

\begin{figure}[ht!]
\caption{Comparison of first- and second- pass visual spectral classification of the 92 spectra with evidence of M or L spectral classification.  The one-to-one line is shown in long dashes.  Jitter has been added to the spectral subtypes to ease comparison of multiple overlapping sources.  The color bar indicates the amount by which each spectrum was de-reddened.  \label{fig_dereddened_comparison} }
\centering
\includegraphics[scale=0.5]{chIMACS/figures/dereddened_spt_comparison}
\end{figure}

@@

\begin{figure}[ht!]
  \caption{Na~I 8190 equivalent width as a function of spectral type from M0 to L5.  The sequence shows a clear bifurcation, splitting into groups of relatively high surface gravity (dwarfs, red points at the top), and low surface gravity (giants, blue points at the bottom).  Objects classified as intermediate gravity \citep{2009AJ....137.3345C} are shown as purple circles.  Young 10$-$20 Myr sources in the Beta Pictoris moving group (BPMG, \citet{2012AJ....143..114S}) are shown as large orange circles.  The dotted black line shows the median of the field dwarfs in Rizzo.  The solid black line excludes 90\% of the field objects, and defines our criterion for Na~I EW indicative of youth.  The green squares are young brown dwarf candidates from this work that meet the youth criterion.  The brown triangles are sources that do not meet the criterion for youth.\label{fig_NaI_EW} }
\centering
\includegraphics[scale=0.6]{chIMACS/figures/NaI_EW}
\end{figure}

@@

\begin{figure}[ht!]
  \caption{Pre main sequence HR diagram indicating membership of new young very low mass stars and brown dwarfs to \emph{Ophiuchus}.  The green circles are members based in part on their position in this diagram.  The red squares are sources without evidence for membership, or evidence of non-membership.  Sources OPH\_349 and OPH\_2 are edge-on disks, based on the presence of mid-IR excess, suppressed near-IR and optical colors, and their apparent position below the main sequence in this diagram. \label{fig_HRD_NaI_Ex} }
\centering
\includegraphics[scale=0.6]{chIMACS/figures/HRD_zoom.pdf}
\end{figure}

@@

\begin{figure}[ht!]
  \caption{ Spectral energy distributions of 9 members with spectral types M5$-$M6.  The gray circles show the observed photometry.  The green squares show the photometry corrected for the extinction value derived from the first-pass spectral typing.  Both the observed and extinction-corrected photometric data have been normalized by the extinction-corrected $H-$band measurement.  The red dotted line shows the blackbody with temperature equal to $T_{\mathrm{eff}}$ for each source.  \label{fig_SEDs_9panel} }
\centering
\includegraphics[scale=0.6]{chIMACS/figures/SEDS_9panel}
\end{figure}

\begin{figure}[ht!]
  \caption{ Spectral energy distributions of 7 members with spectral types M6$-$M8.5.  The plots have the same symbols and scaling as in Figure \ref{fig_SEDs_9panel}.  \label{fig_SEDs_7panel} }
\centering
\includegraphics[scale=0.6]{chIMACS/figures/SEDS_7panel}
\end{figure}

@@

\begin{figure}[ht!]
\caption{IMACS spectra of 10 very low mass YSOs or young brown dwarfs towards \emph{Ophiuchus} with spectral types M5-M6.  The sources all demsontrate spectroscopic evidence of youth evinced by their weak Na~I feature at 8200$\angstrom$.  Source 2mx\_10919 is missing the Na~I feature but demonstrates exceptionally large H$\alpha$ attributable to accretion.  The spectra have been Gaussian smoothed with a 7$\angstrom$ kernel bandwidth.  All spectra were corrected for telluric absorption.  The spectra are normalized at 7500 $\angstrom$ and offset by 1 in the vertical direction. \label{fig_IMACS_spectra1} }
\centering
\includegraphics[scale=0.65]{chIMACS/figures/IMACS_spectra_M0_M6}
\end{figure}

\begin{figure}[ht!]
\caption{IMACS spectra of 5 young brown dwarfs with spectral types M6$-$M8.5.  Same scaling as in Figure \ref{fig_IMACS_spectra1}. \label{fig_IMACS_spectra2} }
\centering
\includegraphics[scale=0.65]{chIMACS/figures/IMACS_spectra_M6_M8p5}
\end{figure}

@@

\begin{figure}[ht!]
  \caption{Images of OPH\_349 with the nearby OPH\_26571.  Images are from right to left: MOSAIC $I-$band, $[3.6]$, $[8.0]$.}
\begin{minipage}[b]{0.3\linewidth}
\centering
\includegraphics[scale=0.15]{chIMACS/figures/OPH_349_I_image}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.3\linewidth}
\centering
\includegraphics[scale=0.15]{chIMACS/figures/OPH_349_IRAC1_image}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.3\linewidth}
\centering
\includegraphics[scale=0.15]{chIMACS/figures/OPH_349_IRAC4_image}
\end{minipage}
\end{figure}

\subsection{Mid-IR colors of diskless new members}

We looked at the distributions of the mid-IR slope of our new members distinguish between the diskless and disk-bearing members.  We include in our analysis the mid-IR data of 187 Class I, II, and III Taurus members with spectral types later than M0 \citep{2010ApJS..186..111L}.  The large number of Taurus members allows us to construct a kernel density estimate in a plot of $[3.6]-[8.0]$ versus spectral type, shown in Figure \ref{fig_I1_I4_density}.  The marginal distribution of $[3.6]-[8.0]$ reveals two populations: a presumably diskless group of sources with $[3.6]-[8.0] \sim 0$ and disk-bearing sources with $[3.6]-[8.0] \sim 1.5$.  The valley in-between the disk-bearing and diskless sources can be understood as evidence for a short-lived phase of disk-clearing \citep{2009ApJS..181..321E}.  All of the \citet{allers06} sources (black circles in Figure \ref{fig_I1_I4_density}) were selected for evidence of mid-IR excess, they appear in the upper branch with $[3.6]-[8.0] \sim 1.5$.  Most of our sources (white squares in Figure \ref{fig_I1_I4_density}) appear in the lower branch with $[3.6]-[8.0] \sim 0$.  The source 2MASS J16214199$-$2313432, an M3 \citep{2011ASPC..448..633G}, has $[3.6]-[8.0]=0.79\pm0.2$ placing it in the valley between the two clusters of disk bearing and diskless objects.  This source might be the only ``transition disk'' out of the \citet{allers06} sample and our sample.  Despite being sensitive to them, we find no sources in this valley, a feature that extends into the sub-stellar regime.  We take this observation as evidence that whatever the mechanism for disk-clearing is, it proceeds similarly in the sub-stellar regime as it does for stellar objects.

\begin{figure}[ht!]
  \caption{ Distribution of $[3.6]-[8.0]$ as a function of spectral type for new young stellar and substellar objects in this work (white squares with black edges).  The distribution of 187 Class I, II, and III Taurus members with spectral types later than M0 \citep{2010ApJS..186..111L} is shown as the kernel density estimate contours in the background.  The black circles with white edges are the 8 sources towards \emph{Ophiuchus} from \citet{allers06} with spectral types from \citet{2011ASPC..448..633G}.  The white dashed line is constructed from Class III young stellar and substellar objects in $\eta$ Cha, $\epsilon$ Cha, and TWA \citep{2010ApJS..186..111L}, and represents the photospheric colors of young objects.  The two edge-on disks OPH\_2 and OPH\_349 are outliers in this plot.  The two disk-bearing sources are 2mx\_10919 and 2mx\_14856.  The other 12 members are diskless sources.  \label{fig_I1_I4_density} }
\centering
\includegraphics[scale=0.6]{chIMACS/figures/I1_I4_density.pdf}
\end{figure}

We used the class III analogs in our new sample to construct mid-IR photospheric colors of late-type sources.  \citet{2010ApJS..186..111L} construct the photospheric colors of young objects as a function of spectral type with evolved class III objects in $\eta$ Cha, $\epsilon$ Cha, and TWA\footnote{The original table with these values contains an error, see the erratum in \cite{2010ApJS..189..353L}}.  We extend the relationship of \citet{2010ApJS..186..111L} with more late-type sources by combining our sample with theirs.  The \citet{2010ApJS..189..353L} sample includes 7 Class III sources with spectral type later than M8: J04272799+2612052, J04274538+2357243, J04302365+2359129, J04354526+2737130, J04355143+2249119, J04373705+2331080, J04574903+3015195.  This work adds 3 new Class III sources with spectral types later than M8.  The colors are consistent with the \citet{2010ApJS..189..353L} sample, with a mean $[3.6]-[8.0]=0.3$ for M8.5 spectral types.  For comparison, M0$-$M2 sources have $[3.6]-[8.0]<0.1$.    Figure \ref{fig_midIR_results} shows a close-up on the mid-IR colors of old field dwarfs \citep{2006ApJ...651..502P}, young Taurus members \citep{2010ApJS..186..111L}, and \emph{Ophiuchus} members from \citep{allers06} and this work.  The increasing bifurcation between the background density of Taurus Class II and Class III sources as a function of wavelength can be understood as the mid-IR excess detaching from the photosphere.

>>>>

\chapter{Evolved disk population of young brown dwarfs towards \emph{Ophiuchus}}

@@

\begin{figure}[ht!]
\caption[Map of the region of \emph{Ophiuchus} targeted in our survey]{Map of the region targeted by our survey.  The background grayscale image is the 2MASS NICER extinction map \citep{2008A&A...489..143L} from the COMPLETE project \citep{2006AJ....131.2921R}.  The solid line boundaries outline our regions of custom photometry with the following color scheme: \emph{blue solid lines} for the ISPI $JH$ catalog, \emph{green} for ISPI $K-$band, \emph{red} for \emph{c2deep}, \emph{magenta} for $I-$band, and \emph{yellow} for the custom $W-$band.  The large \emph{blue dashed} box defines our 2MASS $JH$ catalog.  The markers concentrated toward the right side of the image are from from previous surveys of \emph{Upper Scorpius}, with \emph{yellow squares:} \cite{2006AJ....131.3016S}.  \emph{Ophiuchus} members are concentrated around the high extinction core to the left of the image.  All known brown dwarfs detected by \emph{Herschel} are shown as \emph{green upward pointing triangles}, while brown dwarfs not detected by \emph{Herschel} are \emph{red downward pointing triangles}, \cite{2013A&A...559A.126A}. \emph{Cyan} circles are from \citet{2010ApJ...720.1374H}, and blue diamonds are from \citet{allers06}.\label{fig_star_chart}}
\centering
\includegraphics[scale=0.5]{chIMACS/figures/Ophiuchus_map}
\end{figure}

@@

\subsubsection{$W-$ filter}
Allers et al. (in prep) designed and implemented a custom filter centered at 1.4 $\mu$m, intermediate between the $J-$ and $H-$ atmospheric windows.  This filter is about 0.2 $\mu$m wide, cutting on near the long end of $J$ and cutting off near the short end of $H$.  This photometric band was designed to distinguish between the photospheric emission of late M and L spectral types and that of reddened FGK and early M spectral types.  Cool stars and brown dwarfs with late M spectral types demonstrate intrinsic water absorption in their photospheres.  There is a strong water absorption band centered around 1.4 $\mu$m.  The filter can also distinguish high$-z$ galaxies, which will not demonstrate intrinsic photospheric water absorption as brown dwarfs do.  The broad-band IJHK colors for FGK and early M sources are indistinguishable, while the $W-$filter band photometry shows a deficit in M-type spectra (Allers et al. \emph{in prep}).

@@

\input{chIMACS/tables/tbl_photomCatalog.tex}

@@

\begin{figure}[ht!]
  \caption[Photometric selection color-color cuts in $I-J$ vs $J-H$]{Color-color cuts in $I-J$ vs $J-H$. The horizontal dashed line shows $I-J=2.85$.  The tilted dotted line demonstrates the selection for intrinsic blue $J-H$ colors ($<0.84156$), allowing for reddening.  The grayscale Hess diagram in the background shows the density of points in each color bin, constructed from 34469 sources with $I-$band detections.  The points in the upper left quadrant of the diagram meet the color cuts 2 and 3 from the list in Section \ref{sec_NIR_selection}.  The magenta circles are sources from \citet{allers06} that have spectral types between M6 and L2 \citep{2011ASPC..448..633G}.\label{fig_NIR_selection_JH}}
\centering
\includegraphics[scale=0.6]{chIMACS/figures/NIR_selection_allers_M6_L2}
\end{figure}

@@

\begin{figure}[ht!]
  \caption[Photometric selection color-color cuts in $I-J$ vs $J-K$]{Color-color cuts in $I-J$ vs $J-K$. The horizontal dashed line shows $I-J=2.85$.  The tilted dotted line demonstrates the selection for intrinsic blue $J-K$ colors ($<1.37662$), allowing for reddening.  The grayscale Hess diagram in the background shows the density of points in each color bin, constructed from 19733 sources with both $I-$ and $K-$band detections.  The points in the upper left quadrant of the diagram meet the color cuts 2 and 4 from the list in Section \ref{sec_NIR_selection}.  The square boxes plotted are sources from \citet{allers06} which have spectral types between M6 and L2 \citep{2011ASPC..448..633G}.\label{fig_NIR_selection_JK}}
\centering
\includegraphics[scale=0.6]{chIMACS/figures/NIR_selection_JK_allers_M6_L2}
\end{figure}

@@

\begin{figure}[ht!]
  \caption[$H-$band magnitude selection criterion]{$H-$band Magnitude cut.  The horizontal dashed line shows $H=13.99$.  The grayscale Hess diagram in the background shows the density of points in each color-magnitude bin, constructed from the entire 54373 point ISPI deep $JH$ source catalog.  The circles are sources from \citet{allers06} towards \emph{Ophiuchus}.  The two \citet{allers06} sources with $H>13.99$ have M8 spectral types, while the others are M6 or earlier \citep{2011ASPC..448..633G}. \label{fig_NIR_selection_H}}
\centering
\includegraphics[scale=0.6]{chIMACS/figures/NIR_selection_H_allers_oph}
\end{figure}

@@

\begin{figure}[ht!]
  \caption[Mid-infrared color selection]{$[3.6]-[5.8]$ vs $[3.6]-[8.0]$ color plot, demonstrating the mid-IR excess selection criterion.  The grayscale Hess diagram shows the density of 14095 sources in our sample possessing a 2 $\sigma$ detection in $[3.6]$ and a 2$\sigma$ detection in at least one of $[5.8]$, $[8.0]$, or $[24]$.  The horizontal dashed line is $[3.6]-[8.0]=0.21$, the vertical line is $[3.6]-[8.0]=0.08$ \citep{2006ApJ...651..502P}.  Sources meeting the criteria described in Section \ref{sec_midIR_selection} are primarily in the upper right quadrant.  Some sources with 3$\sigma$ $[24]$ detections are in the other quadrants.  The large colored circles are all sources from \citet{allers06}. \label{fig_midIR_selection}}
\centering
\includegraphics[scale=0.6]{chIMACS/figures/disk_selection_allers}
\end{figure}

@@

\begin{figure}[ht!]
	\caption[$W-$filter selection method]{Histogram of the $Q$ value derived from $W-$band photometry.  The vertical dashed lines represent the boundaries of the selection method.  The dark colored region region interior to the boundaries indicates the 4\% of sources that were both detected in $W-$band and met the selection criteria.  The measured $Q-$values had to be at least 2$\;\sigma$ within the boundaries on either side, excluding some low-signal to noise ratio sources with nominal values between the boundaries and causing the blue shaded histogram to be below the light shaded parent population histogram.  \label{fig_Q_value_histogram}}
\centering
\includegraphics[scale=0.6]{chIMACS/figures/W_phot_sel_mgs}
\end{figure}

@@

\begin{figure}[ht!]
  \caption[Mid-infrared photospheric emission selection]{$H-[3.6]$ and $K-[3.6]$ color cuts that comprise the ``mid-IR photosphere'' criterion.  \emph{Left panel-} The gray histrograms show the distribution of the 42268 sources in the catalog with a $[3.6]$ measurement, while the colored histogram shows the distribution of sources with $H-[3.6]$ \emph{consistent with} 0.8 (dashed vertical line) or greater.  The right panel shows an additional and more restrictive color cut applied only to the 18420 sources detected in both $K-$ band and $[3.6]$: these sources had to have $K-[3.6]$ exceed 0.49 (vertical dashed line) by 1 $\sigma$.  The final ``mid-IR photosphere criterion'' is the union of the color cuts in the left and right panels if $K-$band exists, otherwise it is just the sources satisfying the left panel.  \label{fig_midIR_phot_sel}}
\centering
\includegraphics[scale=0.6]{chIMACS/figures/midIR_phot_sel}
\end{figure}

@@

\begin{landscape}
	\input{chIMACS/tables/tbl_IMACSslitMasks.tex}
\end{landscape}

@@

\begin{figure}[ht!]
\caption[Comparison of IMACS spectroscopy to a previously published spectrum of the same source]{Direct comparison spectra of the M7.25 young brown dwarf OPH1622-2405a, observed with IMACS from this work (solid blue line), and provided by K. Luhman (dotted black line, \citet{2007ApJ...659.1629L}).  The regions of telluric atmospheric absorption are indicated with light gray vertical bands.  \label{fig_oph1622_compare}}
\centering
\includegraphics[scale=0.9]{chIMACS/figures/oph1622-2405a_compare}
\end{figure}

@@

\begin{figure}[ht!]
\caption[Effect of reddening on spectral classification]{Comparison of first- and second- pass visual spectral classification of the 92 spectra with evidence of M or L spectral classification.  The one-to-one line is shown in long dashes.  Jitter has been added to the spectral subtypes to ease comparison of multiple overlapping sources.  The color bar indicates the amount by which each spectrum was de-reddened.  \label{fig_dereddened_comparison} }
\centering
\includegraphics[scale=0.5]{chIMACS/figures/dereddened_spt_comparison}
\end{figure}

@@

\begin{figure}[ht!]
  \caption[Na~I 8190 equivalent width as a function of spectral type from M0 to L5]{Na~I 8190 equivalent width as a function of spectral type from M0 to L5.  The sequence shows a clear bifurcation, splitting into groups of relatively high surface gravity (dwarfs, red points at the top), and low surface gravity (giants, blue points at the bottom).  Objects classified as intermediate gravity \citep{2009AJ....137.3345C} are shown as purple circles.  Young 10$-$20 Myr sources in the Beta Pictoris moving group (BPMG, \citet{2012AJ....143..114S}) are shown as large orange circles.  The dotted black line shows the median of the field dwarfs in Rizzo.  The solid black line excludes 90\% of the field objects, and defines our criterion for Na~I EW indicative of youth.  The green squares are young brown dwarf candidates from this work that meet the youth criterion.  The brown triangles are sources that do not meet the criterion for youth.\label{fig_NaI_EW} }
\centering
\includegraphics[scale=0.6]{chIMACS/figures/NaI_EW}
\end{figure}

@@

\begin{figure}[ht!]
  \caption[Pre main sequence HR diagram with young very low mass stars and brown dwarfs]{Pre main sequence HR diagram indicating membership of young very low mass stars and brown dwarfs to \emph{Ophiuchus}.  The green circles are members based in part on their position in this diagram.  The red squares are sources without evidence for membership, or evidence of non-membership.  Sources OPH\_349 and OPH\_2 are edge-on disks, based on the presence of mid-IR excess, suppressed near-IR and optical colors, and their apparent position below the main sequence in this diagram. \label{fig_HRD_NaI_Ex} }
\centering
\includegraphics[scale=0.6]{chIMACS/figures/HRD_zoom.pdf}
\end{figure}

@@

\begin{figure}[ht!]
  \caption[Spectral energy distributions of nine members of \emph{Ophiuchus}]{Spectral energy distributions of 9 members with spectral types M5$-$M6.  The gray circles show the observed photometry.  The green squares show the photometry corrected for the extinction value derived from the first-pass spectral typing.  Both the observed and extinction-corrected photometric data have been normalized by the extinction-corrected $H-$band measurement.  The red dotted line shows the blackbody with temperature equal to $T_{\mathrm{eff}}$ for each source.  \label{fig_SEDs_9panel} }
\centering
\includegraphics[scale=0.5]{chIMACS/figures/SEDS_9panel}
\end{figure}

\begin{figure}[ht!]
  \caption[Spectral energy distributions of seven members of \emph{Ophiuchus}]{Spectral energy distributions of 7 members with spectral types M6$-$M8.5.  The plots have the same symbols and scaling as in Figure \ref{fig_SEDs_9panel}.  \label{fig_SEDs_7panel} }
\centering
\includegraphics[scale=0.5]{chIMACS/figures/SEDS_7panel}
\end{figure}

@@

\begin{figure}[ht!]
\caption[IMACS spectra of 10 very low mass YSOs or young brown dwarfs towards \emph{Ophiuchus} with spectral types M5-M6]{IMACS spectra of 10 very low mass YSOs or young brown dwarfs towards \emph{Ophiuchus} with spectral types M5-M6.  The sources all demsontrate spectroscopic evidence of youth evinced by their weak Na~I feature at 8200$\angstrom$.  Source 2mx\_10919 is missing the Na~I feature but demonstrates exceptionally large H$\alpha$ attributable to accretion.  The spectra have been Gaussian smoothed with a 7$\angstrom$ kernel bandwidth.  All spectra were corrected for telluric absorption.  The spectra are normalized at 7500 $\angstrom$ and offset by 1 in the vertical direction. \label{fig_IMACS_spectra1} }
\centering
\includegraphics[scale=0.65]{chIMACS/figures/IMACS_spectra_M0_M6}
\end{figure}

\begin{figure}[ht!]
\caption[IMACS spectra of 5 young brown dwarfs with spectral types M6$-$M8.5]{IMACS spectra of 5 young brown dwarfs with spectral types M6$-$M8.5.  Same scaling as in Figure \ref{fig_IMACS_spectra1}. \label{fig_IMACS_spectra2} }
\centering
\includegraphics[scale=0.65]{chIMACS/figures/IMACS_spectra_M6_M8p5}
\end{figure}

@@

\begin{figure}[ht!]
  \caption[Images of an edge-on disk source with nearby source]{Images of OPH\_349 with the nearby OPH\_26571.  Images are from right to left: MOSAIC $I-$band, $[3.6]$, $[8.0]$.}
\begin{minipage}[b]{0.3\linewidth}
\centering
\includegraphics[scale=0.15]{chIMACS/figures/OPH_349_I_image}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.3\linewidth}
\centering
\includegraphics[scale=0.15]{chIMACS/figures/OPH_349_IRAC1_image}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.3\linewidth}
\centering
\includegraphics[scale=0.15]{chIMACS/figures/OPH_349_IRAC4_image}
\end{minipage}
\end{figure}

\subsection{Mid-IR colors of diskless members}

We looked at the distributions of the mid-IR slope of our sample to distinguish between the diskless and disk-bearing members.  We include in our analysis the mid-IR data of 187 Class I, II, and III Taurus members with spectral types later than M0 \citep{2010ApJS..186..111L}.  The large number of Taurus members allows us to construct a kernel density estimate in a plot of $[3.6]-[8.0]$ versus spectral type, shown in Figure \ref{fig_I1_I4_density}.  The marginal distribution of $[3.6]-[8.0]$ reveals two populations: a presumably diskless group of sources with $[3.6]-[8.0] \sim 0$ and disk-bearing sources with $[3.6]-[8.0] \sim 1.5$.  The valley in-between the disk-bearing and diskless sources can be understood as evidence for a short-lived phase of disk-clearing \citep{2009ApJS..181..321E}.  All of the \citet{allers06} sources (black circles in Figure \ref{fig_I1_I4_density}) were selected for evidence of mid-IR excess, they appear in the upper branch with $[3.6]-[8.0] \sim 1.5$.  Most of our sources (white squares in Figure \ref{fig_I1_I4_density}) appear in the lower branch with $[3.6]-[8.0] \sim 0$.  The source 2MASS J16214199$-$2313432, an M3 \citep{2011ASPC..448..633G}, has $[3.6]-[8.0]=0.79\pm0.2$ placing it in the valley between the two clusters of disk bearing and diskless objects.  This source might be the only ``transition disk'' out of the \citet{allers06} sample and our sample.  Despite being sensitive to them, we find no sources in this valley, a feature that extends into the sub-stellar regime.  We take this observation as evidence that whatever the mechanism for disk-clearing is, it proceeds similarly in the sub-stellar regime as it does for stellar objects.

\begin{figure}[ht!]
  \caption[$[3.6]-[8.0]$ as a function of spectral type for young stellar and substellar objects]{ Distribution of $[3.6]-[8.0]$ as a function of spectral type for young stellar and substellar objects in this work (white squares with black edges).  The distribution of 187 Class I, II, and III Taurus members with spectral types later than M0 \citep{2010ApJS..186..111L} is shown as the kernel density estimate contours in the background.  The black circles with white edges are the 8 sources towards \emph{Ophiuchus} from \citet{allers06} with spectral types from \citet{2011ASPC..448..633G}.  The white dashed line is constructed from Class III young stellar and substellar objects in $\eta$ Cha, $\epsilon$ Cha, and TWA \citep{2010ApJS..186..111L}, and represents the photospheric colors of young objects.  The two edge-on disks OPH\_2 and OPH\_349 are outliers in this plot.  The two disk-bearing sources are 2mx\_10919 and 2mx\_14856.  The other 12 members are diskless sources.  \label{fig_I1_I4_density} }
\centering
\includegraphics[scale=0.6]{chIMACS/figures/I1_I4_density.pdf}
\end{figure}

We used the class III analogs in our sample to construct mid-IR photospheric colors of late-type sources.  \citet{2010ApJS..186..111L} construct the photospheric colors of young objects as a function of spectral type with evolved class III objects in $\eta$ Cha, $\epsilon$ Cha, and TWA\footnote{The original table with these values contains an error, see the erratum in \cite{2010ApJS..189..353L}}.  We extend the relationship of \citet{2010ApJS..186..111L} with more late-type sources by combining our sample with theirs.  The \citet{2010ApJS..189..353L} sample includes 7 Class III sources with spectral type later than M8: J04272799+2612052, J04274538+2357243, J04302365+2359129, J04354526+2737130, J04355143+2249119, J04373705+2331080, J04574903+3015195.  This work adds 3 new Class III sources with spectral types later than M8.  The colors are consistent with the \citet{2010ApJS..189..353L} sample, with a mean $[3.6]-[8.0]=0.3$ for M8.5 spectral types.  For comparison, M0$-$M2 sources have $[3.6]-[8.0]<0.1$.    Figure \ref{fig_midIR_results} shows a close-up on the mid-IR colors of old field dwarfs \citep{2006ApJ...651..502P}, young Taurus members \citep{2010ApJS..186..111L}, and \emph{Ophiuchus} members from \citep{allers06} and this work.  The increasing bifurcation between the background density of Taurus Class II and Class III sources as a function of wavelength can be understood as the mid-IR excess detaching from the photosphere.

\begin{figure}[ht!]
  \caption[Mid-IR colors as a function of spectral type for our sample]{Mid-IR colors as a function of spectral type for our sample.  Young stellar and substellar objects in this work are white squares with black edges and error bars.  The distribution of 187 Class I, II, and III Taurus members with spectral types later than M0 \citep{2010ApJS..186..111L} is shown as the kernel density estimate contours in the background.  The black circles with white edges are the 8 sources towards \emph{Ophiuchus} from \citet{allers06} with spectral types from \citet{2011ASPC..448..633G}.  The white dashed line is constructed from Class III young stellar and substellar objects in $\eta$ Cha, $\epsilon$ Cha, and TWA \citep{2010ApJS..186..111L}, and represents the photospheric colors of young objects.  The photospheric colors of field dwarfs from \citet{2006ApJ...651..502P} are shown as blue diamonds. 
  The increasing dichotomy between the background density of Taurus members as a function of wavelength can be understood as the mid-IR excess detaching from the photosphere.  The Taurus members and \citet{allers06} members have not been corrected for extinction.  \label{fig_midIR_results} }
\centering
\includegraphics[scale=0.6]{chIMACS/figures/midIR_phot_results.pdf}
\end{figure}
